---
title: "Assignment 2."
author: "Kowsick Ram"
date: "2022-11-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1.	Sort flights to find the fastest flights
```{r}
arrange(flights,arr_time)
```
2.	Compare dep_time, sched_dep_time, and dep_delay. How would you expect those three numbers to be related?
```{r}
select(flights,dep_time,shed_dep_time,dep_delay)
```
3.	Brainstorm at least 5 different ways to assess the typical delay characteristics of a group of flights. Consider the following scenarios:
a.	A flight is 15 minutes early 50% of the time, and 15 minutes late 50% of the time.
b.	A flight is always 10 minutes late.
c.	A flight is 30 minutes early 50% of the time, and 30 minutes late 50% of the time.
d.	99% of the time a flight is on time. 1% of the time it’s 2 hours late.
```{r}
str(flights)
head(flights)
flight_delay_summary <- group_by(flights, flight) %>% summarise(num_flights = n(),
                                                                percentage_on_time = sum(arr_time == sched_arr_time)/num_flights,
                                                                percentage_early = sum(arr_time < sched_arr_time)/num_flights, 
                                                                percentage_15_mins_early = sum(sched_arr_time - arr_time == 15)/num_flights,
                                                                percentage_late = sum(arr_time > sched_arr_time)/num_flights,
                                                                percentage_15_mins_late = sum(arr_time - sched_arr_time == 15)/num_flights,
                                                                percentage_2_hours_late = sum(arr_time - sched_arr_time == 120)/num_flights)

```
4.	Which plane (tailnum) has the worst on-time record?
```{r}
arrange(flights,desc(arr_delay),desc(dep_delay))
```
5.	Brainstorm as many ways as possible to select dep_time, dep_delay, arr_time, and arr_delay from flights.
```{r}
select(flights,dep_time,dep_delay,arr_time,arr_delay)
select(flights,4,6,7,9)
select(flights,starts_with("dep"),starts_with("arr_"))
select(flights,ends_with("_time"),ends_with("_delay"))
c(shed_arr_time,sched_dep_time,air_time)
```


